---
pagetitle: "spc"
---

## Statistical Process Control (SPC)

Bamako Lightening is a company that manufactures lamps. The weight of each lamp is critical to the quality of the product. The Production Operator monitors the production process using xbar and R-charts. Samples are taken of six lamps every hour and their means and ranges plotted on control charts. 

We start by loading it in our R session:
```{r message = FALSE}
bamako <- read_csv("data/Bamako.csv")
```

The data in Figure 7.12 below represents samples taken over a period of 25 hours of production.

```{r}
knitr::kable(head(bamako), caption = "Figure 7.12")
```


### xbar and  R charts

To plot the control chart we can use the qcc package.
```{r}
library(qcc)
```

Before entering regular production it is recommended to run a "calibration run". The calibration run is used to calculate the control limits. 

```{r }
qcc(bamako[1:5,], type = "xbar")
```
Afterwards, the production samples can  be assessed against those limits and the control chart rules can be verified. In this example the shewhart rules are used.



In the graphic below the control limits are calculated according to the selected duration of the calibration run. The runs breaking the shewhart rules are re-evaluated when control limits change.

Adapted from [@Bass2007]