---
pagetitle: "Joao Ramalho"
---

```{r setup, echo = FALSE, message=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(htmltools)

# original headers color: #337AB7
```

```{r}
div(
  br(),
  img(
    style="display:inline;",
    src = "img/JR.png",
    alt = "Jo\u00E3o Ramalho",
    style = "border-radius: 100%"
  ),
  div(
    h1("Jo\u00E3o Ramalho"),
    h2("Industrial Data Scientist")
  )
)

```

<br>

### About me

I'm an Industrial Data Scientist and my main interests are in:

* Design of Experiments
* Measurement Science
* Process Control

I am active in the in the manufacturing industry since 22 years, starting with Philip Morris, then Rolex and now with Nestlé. Having held numerous positions in R&D, Operations and IT I have a broad understanding of how consumer goods are conceived, industrialized and manufactured.

My background is Mechanical Engineering from the [IST](http://ist.pt/) with a Project Management certification from [PMI](https://www.pmi.org/) and a Data Science certification from [DataCamp](https://www.datacamp.com/). Currently I'm specializing in Data Visualization at the Swiss technical university [EPFL](https://www.extensionschool.ch/).
